\section{Related Work}

\textit{Ray Locality.} Pharr et al. ~\cite{Pharr:1997:RCS:258734.258791} observed that primary rays and simple light rays exhibit ray locality but chose not to further explore this type of locality. Boulos et al.~\cite{Boulos2008AdaptiveRP} worked on pre-processing rays in the ray pool to accelerate ray traversal, however, their technique is limited to offline rendering and infeasible for online rendering. Wald et al \cite{doi:10.1111/1467-8659.00508, Wald07simdray} use ray locality for packet tracing but do not skip redundant computations.

\textit{GPU BVH Traversal.} Aila and Laine ~\cite{Aila:2009:UER:1572769.1572792} provided the most widely used GPU benchmark for ray traversal. Aila and Kerras ~\cite{Aila:2010:ACT:1921479.1921497} propose to reduce the memory traffic during tree traversal via changes to the GPU architecture to facilitate treelet compaction. Aila and Laine's GPU ray tracing benchmark has been further extended recently by Ylitie et al. ~\cite{Ylitie:2017:EIR:3105762.3105773} where the compression of the memory traffic from an 8-wide BVH improved performance by a factor of up to 3.3 due to memory reduction. Lier et al. ~\cite{Lier:2018:CSR:3231578.3231583} applied SIMD style ray tracing to wide BVH trees to improve incoherent ray traversal performance by 35\%-45\% on average. 

\textit{Harware Accelerated Ray Tracing.} Shkurko et al. ~\cite{Shkurko:2017:DSH:3105762.3105771} achieved performance gains by buffering rays inside the acceleration structure, thereby achieving perfect prefetching and avoiding duplicate memory fetches. Their technique assumes custom MIMD hardware and fixed function logic. More recently, Lu et al. ~\cite{Lu:2017:UPG:3123939.3124532} made changes to the GPU SIMD architecture to minimize thread divergence to improve traversal speed. Thread divergence was avoided by preventing certain threads in warps from intersecting scene data, while others are traversing or fetching new ray data.

\textit{Ray tracing APIs.} Recently ray tracing graphics APIs have enjoyed much progress. Embree ~\cite{Wald:2014:EKF:2601097.2601199} is a highly optimized CPU path tracer, OptiX ~\cite{Parker:2010:OGP:1833349.1778803} is it's GPU counterpart. Microsoft announced the DXR API ~\cite{MicrosoftDXR} which was used recently by EA ~\cite{Haines2019} in a hybrid real-time rendering demo producing great visual accuracy at interactive frame rates.
